\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing economic inequality with tax data - Switzerland from 1945 to 2010}

### 2014-07-01 paper/paper.tex
compile-o-mat now with visible tables

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
## Smoothing using 0.4
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/reldist20032010}

@@

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Loading required package: splines}}\end{kframe}% latex.default(format(c(`Median Index` = med, `Lower Index` = lower,      `Upper Index` = upper, `$\\Delta$ Gini` = dgini), digits = ndig),      file = "", title = title) 
%
\begin{table}[!tbp]
\begin{center}
\begin{tabular}{ll}
\hline\hline
\multicolumn{1}{l}{Inequality Indices}&\multicolumn{1}{c}{}\tabularnewline
\hline
Median Index&0.058\tabularnewline
Lower Index&0.072\tabularnewline
Upper Index&0.045\tabularnewline
$\Delta$ Gini&0.025\tabularnewline
\hline
\end{tabular}
\end{center}
\end{table}

@@

% latex.default(format(c(`Median Index` = med, `Lower Index` = lower,      `Upper Index` = upper, `$\\Delta$ Gini` = dgini), digits = ndig),      file = "", title = title) 
%
\begin{table}[!tbp]
\begin{center}
\begin{tabular}{ll}
\hline\hline
\multicolumn{1}{l}{Inequality Indices}&\multicolumn{1}{c}{}\tabularnewline
\hline
Median Index&0.020\tabularnewline
Lower Index&0.029\tabularnewline
Upper Index&0.010\tabularnewline
$\Delta$ Gini&0.013\tabularnewline
\hline
\end{tabular}
\end{center}
\end{table}

@@

% latex.default(format(c(`Median Index` = med, `Lower Index` = lower,      `Upper Index` = upper, `$\\Delta$ Gini` = dgini), digits = ndig),      file = "", title = title) 
%
\begin{table}[!tbp]
\begin{center}
\begin{tabular}{ll}
\hline\hline
\multicolumn{1}{l}{Inequality Indices}&\multicolumn{1}{c}{}\tabularnewline
\hline
Median Index&0.170\tabularnewline
Lower Index&0.206\tabularnewline
Upper Index&0.134\tabularnewline
$\Delta$ Gini&0.044\tabularnewline
\hline
\end{tabular}
\end{center}
\end{table}

@@

% latex.default(format(c(`Median Index` = med, `Lower Index` = lower,      `Upper Index` = upper, `$\\Delta$ Gini` = dgini), digits = ndig),      file = "", title = title) 
%
\begin{table}[!tbp]
\begin{center}
\begin{tabular}{ll}
\hline\hline
\multicolumn{1}{l}{Inequality Indices}&\multicolumn{1}{c}{}\tabularnewline
\hline
Median Index&-0.1084\tabularnewline
Lower Index&-0.2155\tabularnewline
Upper Index&-0.0013\tabularnewline
$\Delta$ Gini&-0.0952\tabularnewline
\hline
\end{tabular}
\end{center}
\end{table}

>>>>

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# reldist: Relative Distribution Methods\\\#\# Version 1.6-2 created on 2013-03-03.\\\#\# copyright (c) 2003, Mark S. Handcock, University of California-Los Angeles\\\#\#\ \ For citation information, type citation("{}reldist"{}).\\\#\#\ \ Type help(package="{}reldist"{}) to get started.\\\#\# \\\#\# \\\#\# Attaching package: 'nlme'\\\#\# \\\#\# Das folgende Objekt ist maskiert from 'package:dplyr':\\\#\# \\\#\#\ \ \ \  collapse\\\#\# \\\#\# This is mgcv 1.7-26. For overview type 'help("{}mgcv-package"{})'.}}\begin{verbatim}
## Smoothing using 0.4
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/reldist20032010}

@@

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Loading required package: splines}}\end{kframe}% latex.default(format(c(`Median Index` = med, `Lower Index` = lower,      `Upper Index` = upper, `$\\Delta$ Gini` = dgini), digits = ndig),      file = "", title = title, table.env = FALSE) 
%
\begin{center}
\begin{tabular}{ll}
\hline\hline
\multicolumn{1}{l}{Inequality Indices}&\multicolumn{1}{c}{}\tabularnewline
\hline
Median Index&0.058\tabularnewline
Lower Index&0.072\tabularnewline
Upper Index&0.045\tabularnewline
$\Delta$ Gini&0.025\tabularnewline
\hline
\end{tabular}
\end{center}

@@

% latex.default(format(c(`Median Index` = med, `Lower Index` = lower,      `Upper Index` = upper, `$\\Delta$ Gini` = dgini), digits = ndig),      file = "", title = title, table.env = FALSE) 
%
\begin{center}
\begin{tabular}{ll}
\hline\hline
\multicolumn{1}{l}{Inequality Indices}&\multicolumn{1}{c}{}\tabularnewline
\hline
Median Index&0.020\tabularnewline
Lower Index&0.029\tabularnewline
Upper Index&0.010\tabularnewline
$\Delta$ Gini&0.013\tabularnewline
\hline
\end{tabular}
\end{center}

@@

% latex.default(format(c(`Median Index` = med, `Lower Index` = lower,      `Upper Index` = upper, `$\\Delta$ Gini` = dgini), digits = ndig),      file = "", title = title, table.env = FALSE) 
%
\begin{center}
\begin{tabular}{ll}
\hline\hline
\multicolumn{1}{l}{Inequality Indices}&\multicolumn{1}{c}{}\tabularnewline
\hline
Median Index&0.031\tabularnewline
Lower Index&0.039\tabularnewline
Upper Index&0.022\tabularnewline
$\Delta$ Gini&0.020\tabularnewline
\hline
\end{tabular}
\end{center}

@@

% latex.default(format(c(`Median Index` = med, `Lower Index` = lower,      `Upper Index` = upper, `$\\Delta$ Gini` = dgini), digits = ndig),      file = "", title = title, table.env = FALSE) 
%
\begin{center}
\begin{tabular}{ll}
\hline\hline
\multicolumn{1}{l}{Inequality Indices}&\multicolumn{1}{c}{}\tabularnewline
\hline
Median Index&-0.1084\tabularnewline
Lower Index&-0.2155\tabularnewline
Upper Index&-0.0013\tabularnewline
$\Delta$ Gini&-0.0952\tabularnewline
\hline
\end{tabular}
\end{center}
